Viscous Transport in Eroding Porous Media

### 2019-06-10 docs/transport/erosion_transport.tex
do the section 4.3 in transport paper

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \alpha_\iin 
    \left(\frac{L_i}{N_\iin} \right).
\end{align}

To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.
Therefore, we first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      0 \\ \pm 1
    \end{array}
    \right]
  \right\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
\end{align}
If body $\gamma_i$ satisfies this condition, for each point $\xx \in
\gamma_i$, we apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
\end{align}

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we first compute an accurate solution by using the Barycentric
quadrature rule for all discretization points.  Then, for multiple
values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
with the trapezoid rule for all points that do not satisfy
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = ???$ and $\alpha_\out = ???$ give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.

@@

The initial shape of the eroding body $\gamma_i$ is a circle centered at
$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
$\gamma_i$ is discretized with $N_\iin$ points.  Using the annealing
algorithm described in Section ???, the initial configuration has the
desired initial porosity, and the minimum separation between any pair of
bodies and between the bodies and solid wall is $d$.  A no-slip boundary
condition is imposed on $\gamma$.  To round off inevitable corners on
the eroding bodies, we apply smoothing the smoothing parameters
$\eps=???$ and $\sigma=???$, as described in~\cite{qua-moo2018}, for all
simulations.

@@

Finally, the parameters used to determine if a point uses the trapezoid
or Barycentric quadrature rule are $\alpha_\iin = ???$ and
$\alpha_\out=???$.

>>>>

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
{\color{red}
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right).
\end{align}
}
To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.
Therefore, we first check if
{\color{red}
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_{\cc_i } \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out}
\end{align}
where $x_{\cc_i } $ is the x coordinate of $\cc_i$.}
If body $\gamma_i$ satisfies this condition, for each point {\color{red}$\xx=(x,y) \in
\gamma_i$}, we apply the Barycentric rule to points that satisfy
{\color{red}
\begin{align}
  \label{eqn:PointsWallCutoff}
  \|y \pm 1\| <  \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}}

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we first compute an accurate solution by using the Barycentric
quadrature rule for all discretization points.  Then, for multiple
values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
with the trapezoid rule for all points that do not satisfy
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that {\color{red}$\alpha_\iin = 4$ and $\alpha_\out = 4$ }give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.

@@

The initial shape of the eroding body $\gamma_i$ is a circle centered at
$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
$\gamma_i$ is discretized with $N_\iin$ points.  Using the annealing
algorithm described in Section ???, the initial configuration has the
desired initial porosity, and the minimum separation between any pair of
bodies and between the bodies and solid wall is $d$.  A no-slip boundary
condition is imposed on $\gamma$.  To round off inevitable corners on
the eroding bodies, we apply smoothing the smoothing parameters {\color{red}
$\eps=15/256$ and $\sigma=10/256$,} as described in~\cite{qua-moo2018}, for all
simulations.

@@

Finally, the parameters used to determine if a point uses the trapezoid
or Barycentric quadrature rule are $\alpha_\iin = 4$ and
$\alpha_\out=4$.
